\plaintitle

### 2016-09-12 drafts/labor/complexity.tex
piecework_lit should be kind of done

\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems,
often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed,
just like non--expert teams
\cite{foundry}.

\subsubsubsection{\pieceworkpers}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task'',
argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

@@

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties'',
informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

\topic{Technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers,
generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625,
      skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography

  \clearpage
  \nobalance{}
  }
  \endnotetext{
  \section{Complexity notes}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
    exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing'',
    the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

@@

    \topic{A smaller but growing body of work has reflected on this
    and brought to our attention a number of ethical questions surrounding the
    increasing complexity of crowdwork and the hazards that increasingly arise.}
    \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
    --- working for increasing amounts of time on tasks of growing complexity,
    only to discover that requesters are not willing to pay,
    for instance ---
    but these and other dangers range an enormous landscape
    \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

    \topic{We summarize the work discussed so far in this way:
    researchers of crowdsourcing and on--demand labor in general
    have attempted to find the characteristics which
    enable and stymie successful applications of this form of work,
    and how to get past or around these boundaries.}
    Whether this work has focused on the self (as in the case of ``selfsourcing'')
    or on others (as in \textit{CrowdForge} and \textit{Foundry}),
    crowdsourcing literature has generally studied the constituent work
    and attempted either to work around
    or indeed with
    the limitations of crowdwork to accomplish a difficult task
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

@@

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber,
  where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited,
  we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
}

>>>>

\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems%
, often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers%
, leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge})%
, and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed%
, just like non--expert teams
\cite{foundry}.

\subsubsubsection{\pieceworkpers}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539}%
, who describes piecework as
    ``\dots~based on examination of various shop jobs,
      which included calculation of the standard time and compensation for each task''%
, argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

@@

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties''%
, informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

\topic{Technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers%
, generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625%
,       skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \clearpage
  \nobalance{}
  }

  \endnotetext{
  \section{Complexity notes}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work%
,     exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing''%
,     the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

@@

    \topic{A smaller but growing body of work has reflected on this
    and brought to our attention a number of ethical questions surrounding the
    increasing complexity of crowdwork and the hazards that increasingly arise.}
    \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
    --- working for increasing amounts of time on tasks of growing complexity%
,     only to discover that requesters are not willing to pay%
,     for instance ---
    but these and other dangers range an enormous landscape
    \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

    \topic{We summarize the work discussed so far in this way:
    researchers of crowdsourcing and on--demand labor in general
    have attempted to find the characteristics which
    enable and stymie successful applications of this form of work%
,     and how to get past or around these boundaries.}
    Whether this work has focused on the self (as in the case of ``selfsourcing'')
    or on others (as in \textit{CrowdForge} and \textit{Foundry})%
,     crowdsourcing literature has generally studied the constituent work
    and attempted either to work around
    or indeed with
    the limitations of crowdwork to accomplish a difficult task
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

@@

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber%
,   where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited%
,   we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
}

### 2016-09-12 drafts/labor/decomposition.tex
piecework_lit should be kind of done

\subsubsubsection{\crowdworkpers}
% \ali{Does this belong here at all? The complexity argument just dives in.}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks,
and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work),
the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,
      cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes,
the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT,
and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,
      Cai:2015:WLW:2702123.2702267}.
Yet more work looks at the general framing of tasks,
chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks,
as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested,
we as a community have leaned \textit{into} the peril of
low--context work,
``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

@@

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
\ali{I could point out that the opportunity to check work and
repeat the task is a little like find--fix--verify, but is that jumping the gun?}
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century,
with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result,
the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

@@

  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Slicing notes}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be,
    and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do,
    but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management,
            and how piecework literature tried to measure everything,
            but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}

@@

    \ali{i don't like this section \textit{here}, but i like it in general. what do?}
    \topic{One of the emergent properties of micro--tasks has been the relative cost of
    \textit{finding} worthwhile tasks.}
    The research community has documented and to some extent attempted to intervene in
    the discovery of worthwhile tasks
    \cite{taskSearch}.
    \citeauthor{Cosley:2007:SUI:1216295.1216309}
    attempts to address this by
    directing workers to tasks through
    ``intelligent task routing''
    \cite{Cosley:2007:SUI:1216295.1216309}.
    Much of this work and the work at the periphery of this space, then,
    has focused on
    minimizing the amount of time that people need to spend doing
    anything other than the work for which they are paid.

>>>>

\subsubsubsection{\crowdworkpers}
% \ali{Does this belong here at all? The complexity argument just dives in.}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks%
, and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work)%
, the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes%
, the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT%
, and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996%
,       Cai:2015:WLW:2702123.2702267}.
Yet more work looks at the general framing of tasks%
, chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks%
, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
, we as a community have leaned \textit{into} the peril of
low--context work%
, ``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

@@

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century%
, when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
\ali{I could point out that the opportunity to check work and
repeat the task is a little like find--fix--verify, but is that jumping the gun?}
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century%
, with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out%
, piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result%
, the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

@@

  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Slicing notes}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be%
,     and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do%
,     but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management%
,             and how piecework literature tried to measure everything%
,             but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}

@@

    \ali{i don't like this section \textit{here}, but i like it in general. what do?}
    \topic{One of the emergent properties of micro--tasks has been the relative cost of
    \textit{finding} worthwhile tasks.}
    The research community has documented and to some extent attempted to intervene in
    the discovery of worthwhile tasks
    \cite{taskSearch}.
    \citeauthor{Cosley:2007:SUI:1216295.1216309}
    attempts to address this by
    directing workers to tasks through
    ``intelligent task routing''
    \cite{Cosley:2007:SUI:1216295.1216309}.
    Much of this work and the work at the periphery of this space, then%
,     has focused on
    minimizing the amount of time that people need to spend doing
    anything other than the work for which they are paid.

### 2016-09-12 drafts/labor/flexibility.tex
piecework_lit should be kind of done

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  % \nobalance{}

  \begin{appendices}
  A number of researchers have identified
  worker attrition,
  variability of worker performance,
  and uncertainty about good versus bad--faith actors as open questions of crowdwork
  \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
  \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
  \& workers who are merely responding in kind to bad requesters
  --- and the broader questions surrounding
  the roles that requesters as well as workers should play ---
  but let it suffice to say that
  requesters have been trying to understand and manage what appears to them as inconsistent work.
  Their ways of responding to that variance in work quality has largely involved
  making the work more flexible and resilient to work
  (although some work has gone into investigating the causes, rather than treating the symptoms)}

  Earlier we discussed \citeauthor{cheng2015break}'s work
  measuring the impact that interruption has on worker performance
  \cite{cheng2015break}.
  This work illustrates a broader sentiment in
  both the study and practice
  of crowdwork, that microtasks should be designed resiliently against the variability of workers,
  fully exploiting the abstracted nature of each piece of work
  \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
  That is to say, micro--tasks should be designed such that a single worker's poor performance,
  or a good worker's sudden departure,
  does not significantly impact the agenda of the work as a whole.
  While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
  in the form of higher cumulative time to complete
  (albeit much shorter real time to complete, owing to parallelization),
  \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
  similar tasks together
  \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

  \citeauthor{embracingErrorKrishna} take a different approach;
  by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
  the authors offer orders--of--magnitude improvements
  in various binary classification tasks
  \cite{embracingErrorKrishna}.
  And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
  some researchers have designed work predicated on the expectation of it instead:
  \citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
  crowd workers would never be given enough information to piece together sensitive information about
  any single topic
  \cite{sensitiveTasks}.

  The work thus far seems to attempt to maximize the quality of work among workers through various means:
  \begin{inlinelist}
    \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju},
    \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
    \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
  \end{inlinelist}.

@@

  In the field of piecework,
  the research covering this topic has both explored
  a breadth of tasks that might be rendered doable by piecemeal workers
  \textit{as well as} longitudinally documented the success of these approaches.
  Here, we

\end{appendices}
}

\end{document}

>>>>

\onlyinsubfile{
  % \balance{}
  \printbibliography
  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition%
,     variability of worker performance%
,     and uncertainty about good versus bad--faith actors as open questions of crowdwork
    \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

    Earlier we discussed \citeauthor{cheng2015break}'s work
    measuring the impact that interruption has on worker performance
    \cite{cheng2015break}.
    This work illustrates a broader sentiment in
    both the study and practice
    of crowdwork, that microtasks should be designed resiliently against the variability of workers%
,     fully exploiting the abstracted nature of each piece of work
    \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
    That is to say, micro--tasks should be designed such that a single worker's poor performance%
,     or a good worker's sudden departure%
,     does not significantly impact the agenda of the work as a whole.
    While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
    in the form of higher cumulative time to complete
    (albeit much shorter real time to complete, owing to parallelization)%
,     \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
    similar tasks together
    \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

    \citeauthor{embracingErrorKrishna} take a different approach;
    by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds%
,     the authors offer orders--of--magnitude improvements
    in various binary classification tasks
    \cite{embracingErrorKrishna}.
    And rather than building tasks to \textit{tolerate} worker drop--off and attrition%
,     some researchers have designed work predicated on the expectation of it instead:
    \citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
    crowd workers would never be given enough information to piece together sensitive information about
    any single topic
    \cite{sensitiveTasks}.

    The work thus far seems to attempt to maximize the quality of work among workers through various means:
    \begin{inlinelist}
      \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju}%
,       \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
      \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
    \end{inlinelist}.

@@

    In the field of piecework%
,     the research covering this topic has both explored
    a breadth of tasks that might be rendered doable by piecemeal workers
    \textit{as well as} longitudinally documented the success of these approaches.
    Here, we \ali{\dots?}
}
% \theendnotes
\end{document}
